---
title: "Hobotemp"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hobotemp

This is for managing and understanding your HOBO temperature data

## Requirements

  + [R v4+](https://www.r-project.org/)
  + [dplyr](https://CRAN.R-project.org/package=dplyr)
  + [readr](https://CRAN.R-project.org/package=readr)
  + [stringr](https://CRAN.R-project.org/package=stringr)
  + [ggplot2](https://CRAN.R-project.org/package=ggplot2)
  + [lubridate](https://CRAN.R-project.org/package=lubridate)

## Installation

```
remotes::install_github("rfrancolini/hobotemp")
```

## Function: read_hobotemp()

This function will take in raw hobotemp data and output a csv. Options include whether you want to define a site name (if not, itll pull it from the file name), if you want to define the start/stop times, have it automatically remove the first and last day (default setting), or keep all of the data, and if you want to write a file with a specific output name.

### Read Example Data

```{r example}
library(hobotemp)
x <- read_hobotemp()
x
```

### Read Example Data with User Defined Site

``` {r exampleSiteName}
library(hobotemp)
x <- read_hobotemp(site = "Little Drisko Island")
x
```

### Read Example Data With User Defined Start/Stop Dates

```{r exampleStartStop}
ss <- as.POSIXct(c("2021-05-20", "2021-06-01"), tz = "UTC")
xud <- read_hobotemp(clipped = "user", startstop = ss)
xud
```

## Function: summarize_hobotemp()

Create a dataframe summarizing the temperature data, will group by site.

### Summarize data, csv with one site
```{r ldSummary}
sum1 <- summarize_hobotemp(x)
print.data.frame(sum1)
```

### Summarize data, csv with more than one site
```{r msSummary}
sum2 <- summarize_hobotemp(example_ridge_data())
print.data.frame(sum2)
```

## Function: draw_scatter_plot()

This function will read in a csv of your HOBO data and draw a scatter plot with an overlapping trendline. 

### Draw Example Scatter Plot

```{r tempplot, message=FALSE}
tempplot_x <- draw_scatter_plot(x)
tempplot_x
```

### Draw Example Scatter Plot with User Defined Start/Stop Dates and Title

```{r tempplot_ud, message=FALSE}
tempplot_xud <- draw_scatter_plot(xud, main = "Temperature at Depth, End of May")
tempplot_xud
```

## Function: draw_ridgeline_plot()

This function will create a color-coded ridgeline plot, adapted from [here](https://r-graph-gallery.com/294-basic-ridgeline-plot.html). This will have a line representing the temperature, as well as the space underneath the line colored in using a temperature gradient color scheme. Sites will appear in order they are in dataframe, unless "ordered" option is used.

### Draw example ridgeline plot

```{r ridgeline, message = FALSE}
ridgelineplot <- draw_ridgeline_plot()
ridgelineplot
```

### Draw example ridgeline plot with specified site order (south to north)

```{r ridgelineOrdered, message = FALSE}
SiteOrder <-  c("Cape Liz", "Halfway Rock", "Damariscove", "Isle Au Haut", "Marshall")
ridgelineplotO <- draw_ridgeline_plot(ordered = SiteOrder)
ridgelineplotO
```
